---
title: "Lab 00 - Hello IDS!"
author: "Hannah Teasdale"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Ben", "Teagan", 
           "Tudor", "Hannah"),
  github_username = c("BenHeron5", "Tadnii", 
                      "Tud0rTheGr8", "HannhTeasdale5"), 
  colour = c("#FC2828", "#F3CC17", 
             "#228B22", "#3BA8F7"),
  hobby = c("guitar", "dance", 
            "fencing", "guitar"),
  favourite_number = c(7, 7, 7, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar chart of the favorite numbers of the group.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Number",
          title = "Favorite numbers of the group")
```

Modify axis, legend, and plot labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A list, categorize the date into groups like music or sport.
